|

### 2020-12-09 documents/ovando-etal-assessing-global-fisheries.Rmd
nature comms resubmission

---
title: |
  | Global Assessments of Fishery Status need 
  | Better Data more than Better Models
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yannick Rousseau
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::pdf_document2: default
  bookdown::word_document2:
    reference_docx: word-template.docx
params:
  results_name: ["v1.0"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in tracking the implementation of the United Nations Sustainable Development Goals. While we have reliable estimates of stock status for fisheries accounting for 49% of global catch, our knowledge of the state of the remaining 51%, the world's 'unassessed' fisheries, is poor. Numerous high-profile publications have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methodological differences have produced counterintuitive and conflicting results. Here, we show that despite numerous efforts, our understanding of the status of global fisheries remains poor, even when new sources of broadly available data are added. Obtaining accurate estimates of stock status for the world's fisheries depends on prioritizing the collection of high-priority data at around the globe, rather than the development of new modeling methods alone.
always_allow_html: true
linkcolor: blue
---

@@

<!-- https://www.nature.com/natsustain/about/content -->
<!-- # check in call notes -->

@@

The United Nations Sustainable Development Goal 14 (SDG 14), focusing on "Life under water", calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". Meeting these targets depends in part on our ability to effectively track the status of global marine fish stocks. The Food and Agriculture Organization of the United Nations' (FAO) State of World Fisheries and Aquaculture (SOFIA) report is the most widely used source for tracking the global state of fisheries. As of the most recent report, the FAO estimates that as of 2017 59.6% of marine fish stocks are maximally sustainably fished, 6.2% are underfished, and 34.2% are overfished [@fao2020]. The SOFIA assessment was designed in the 1970s based on the then available data and methods, With the surge in data availability, such as global assessments of management strength, trawl footprints, and fishing effort, and modeling methods, fresh approaches are needed to meet the new demand for tracking progress towards the SDG goals and supporting the research targets set out in the UNited Nations Decade on Oceans and Science plan.

Forty nine percent of landings of marine fishes reported by the FAO are represented in the RAM Legacy Stock Assessment Database [@ricard2012], a repository of best-available estimates of fishery status [@hilborn2020]. The SOFIA process uses these formal assessments for their determinations of stock status wherever possible. However, that leaves 51% of global fisheries landings lacking in formal stock assessments. While these "unassessed" stocks are generally individually smaller than the typically larger and more valuable stocks in the assessed category, collectively they are a vital source of food, employment, cultural value, and ecosystem services around the world.

The SOFIA report bases its estimates of included unassessed stocks mostly on expert opinion. While local experts can be well informed as to the status of their fish stocks, a more quantitative and reproducible process would be desirable, in order to increase reproducibility, transparency, and potential reliability. Numerous studies in recent years have put forward versions of "data-limited" models that have attempted to provide estimates for the global status of these unassessed stocks [@costello2012b; @costello2016a; @pauly2007; @rosenberg2018; @thorson2012a]. Due to data limitations, all of these global assessment efforts use forms of "catch-only" stock assessment models (Free et al. 2020 [@free2020] and references therein). These models seek to infer stock status, for example in terms of biomass *B* relative to the biomass at maximum sustainable yield *B~MSY~*, from characteristics of a fishery's catch history, for example the ratio of catch to maximum catch [@martell2013].

@@

Costello et al. 2016 [@costello2016a] finds similar rankings of regions in terms of stock status as RAM, but their estimate of state of fisheries in the Mediterranean/Black Sea regions and Southeast Asia seem to be over-optimistic, and the Northeast Pacific should be better by comparison. The super-ensemble method [@anderson2017a] used in Rosenberg et al. 2018 [@rosenberg2018] demonstrates the same problem, with stocks in Southeast Asia estimated as doing better than the Northeast Atlantic or Northeast Pacific. The Pauly 2007 [@pauly2007] catch based approach finds the stocks of Southeast Asia in much better condition than the Northeast Pacific or Northeast Atlantic (Table.\@ref(tab:status-tab)). The methods besides RAM in Table.\@ref(tab:status-tab) include both formally assessed and unassessed stocks, and as such we would expect them to differ broadly in their estimates of regional stock status, particularly since we might expect unassessed stocks to be less rigorously managed and by extension have poorer stock status. However, the lack of consistency across heavily assessed regions such as the Northeast Pacific, and the lack of contrast in stock status between heavily and lightly managed regions is concerning.

@@

In this paper we ask, can combining the FAO's catch statistics with other broadly available data improve our understanding of the state of global fisheries? We use a flexible surplus-production based stock assessment software package, [`sraplus`](www.github.com/danovando/sraplus) to demonstrate how different data sources can be used to augment catch-only models at a global scale, and to evaluate how our perception of global stock status would vary depending on which sources of data we include. We show that our understanding of global fishery status is poor, and that improvements depend on a redoubled effort at global data collection and synthesis.

@@

+---------------------------------------------+------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Data Source                                 | Short Name | Data Use                                                                 | Caveats                                                                                                         |
+=============================================+============+==========================================================================+=================================================================================================================+
| Catch data [@fao2020]                       | catches    | Priors on stock status, scaling of population size, exploitation history | Heuristics or regressions used to translate shape of catch history into priors on stock status                  |
+---------------------------------------------+------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Fisheries Management Index [@melnychuk2017] | FMI        | Priors on most recent F/F~MSY~ values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Swept Area Ratio [@amoroso2018]             | SAR        | Priors on most recent F/F~MSY~ values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Reconstructed effort data[@rousseau2019b]   | effort     | Combined with catch data to create an index of abundance                 | Total reconstructed effort across all sectors. Assumed rate of technology creep reported in individual sections |
+---------------------------------------------+------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+

: (\#tab:data) Broadly available data used to inform estimates of global stock status

@@

For our case study, we selected `r n_distinct(exs$stockid)` stocks for which we have stock specific FMI and SAR scores. We then paired effort data at the resolution of year, country, and FAO statistical area from Rousseau et al. 2019 [@rousseau2019] to each stock. As a benchmark, we first estimated stock status for these case study fisheries using the CMSY [@froese2017] method, as this has become one of the most widely used catch-only models currently available. We then used stock-specific data on SAR and FMI to generate priors on F/F~MSY~ for each of the stocks, which were then passed to sraplus. Lastly, we used the reconstructed effort data from [@rousseau2019] to create an index of abundance for each stock, and estimated stock status by fitting to this index while using priors on fishing mortality rates informed by each stock's FMI and SAR values. While CMSY systemically overestimated fishing mortality rates and underestimated stock status, use of the SAR, FMI, and effort data produced substantially more accurate results (Fig.\@ref(fig:cs-plot)).

@@

We next assessed the ability of FMI, SAR, and effort data to improve estimates of global stock status. We based this test on `r ram_comp_data$stockid %>% n_distinct()` fisheries from RAM, covering `r n_distinct(ram_comp_data$isscaap_group)` broad taxonomic groups, with estimates of B/B~MSY~ and greater than 25 years of continuous catch history. B/B~MSY~ values from RAM are themselves estimates, not data, but they are the best available information on global stock status. We then paired the catch histories for these RAM stocks with regional-level SAR, FMI, and effort data. This process approximates a global-level assessment exercise, where data are available at regional levels, but not for specific fisheries.

@@

Performance limitations then are likely to arise less from model misspecification than from the quality of the data themselves. This becomes clearer once we consider the performance of sraplus models fit to combinations of our broadly available datasets. Many of the datasets used produced similar levels of bias as the RAM data (Table.\@ref(tab:perf-tab)). However, this is somewhat an artifact of the data. The status of most stocks in RAM is also relatively good, with recent B/B~MSY~ values generally near one. This means that a model that more or less reproduces the global average of stock status will be relatively unbiased on average, but imprecise. Focusing on MAPE instead, the error of the models jumps dramatically as soon as data other than RAM are used, to a minimum value of `r percent(perf$mape[2])` and a maximum of `r percent(max(perf$mape))`. The mean accuracy across all non-RAM data fits was only `r percent(mean(perf$accuracy[!perf$"Data Used" %in% c("ram-data","guess")]))`. Note that there are only three bins in the FAO stock status classifications, and a "model" that randomly assigns a stock to a status category has a mean accuracy of `r percent(perf$accuracy[perf$"Data Used" == "guess"])`.

@@

```{r mpe-map, fig.width=8, fig.height=8, fig.cap="Median percent error in most recent B/B~MSY~ by FAO statistical area from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or wept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}
ram_mpe_map_plot
```

```{r mape-map, fig.cap = "Median absolute percent error in most recent B/B~MSY~ by FAO statistical area from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or wept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}
ram_mape_map_plot
```

```{r acc-map, fig.cap="Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or wept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}

@@

Global-level assessment are critical for guiding management agendas for the world's oceans, and tracking critical indicators such as the United Nations Sustainable Development Goals. Despite this need, and despite advances in stock assessment methods and available data, we show that our understanding of the world's fisheries remains murky in many parts of the world. While in some cases addition of globally available data, such as quality of fisheries management or effort reconstructions, provided value above and beyond catch histories alone (Fig.\@ref(fig:cs-plot)), at the global level models fit using each of the available datasets, besides the RAM-derived indices, produced biased and imprecise estimates of stock status, frequently performing worse than a simple guess (Table.\@ref(tab:perf-tab)).

@@

We chose to test the performance of methods against estimated values reported in RAM. A reasonable critique of this choice is that unassessed stocks, on which these methods would actually be used, are likely to have vastly different dynamics than the heavily managed stocks in RAM. The clear and systemically poor performance of the methods tested here when applied to RAM stocks would require though that these methods have massively lower bias and higher accuracy for unassessed fisheries than RAM stocks if they are to be expected to provide reasonable picture of global stock status. Free et al. 2020's [@free2020] simulation testing of the types of methods included here suggests that this is unlikely to be true. z

@@

Our value-of-information analysis also shows though the high utility of having access to even a recent snapshot of F/F~MSY~ (Fig.\@ref(fig:voi-plot)). Swept area ratios, Fisheries Management Index scores, or other similar metrics can be used to construct priors on fishing mortality rates, though care must be taken in applying them at the appropriate spatial resolution. Another avenue would be to prioritize the development of a global repository for length and age composition data. Given appropriate conditions, these length measurements can be used to estimate local fishing mortality rates [@hordyk2016; @prince2019; @rudd2017]. While length-based assessments come with a host of assumptions and pitfalls, properly implemented in some fisheries with appropriate life histories these methods may provide an overlooked source of information on fisheries at a global scale, at least as an improvement over relying on catch-only or regional proxies alone. Such a database could be used to construct stock or stock complex specific priors on fishing mortality for particular regions around the globe, which could meaningfully improve our understanding of global fisheries, particularly when paired with catch data and where possible indices of abundance [@thorson2015f;@rudd2017].

@@

The core of our model is a Pella-Tomlinson [@pella1969] production model  in the manner of @winker2018. While models of these kinds abstract away many important details of fish biology and fleet behavior, they are the highest resolution model that the potential data evaluated here will support.

>>>>

---
title: |
  | Status of Global Unassessed Fisheries will Remain Highly Uncertain
  | without Better Data
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yannick Rousseau
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature-communications.csl
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
  bookdown::word_document2:
    reference_docx: SA_MS_Template_2020.docx
params:
  results_name: ["v1.0"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in tracking the implementation of the United Nations Sustainable Development Goals. While we have reliable estimates of stock status for fisheries accounting for approximately half of recent global catch, our knowledge of the state of the majority of the word's 'unassessed' fisheries remains highly uncertain. Numerous high-profile publications have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methodological differences have produced counterintuitive and conflicting results. Here, we show that despite numerous efforts, our understanding of the status of global fisheries remains incomplete, even when new sources of broadly available data are added. Obtaining accurate estimates of stock status for the world's fisheries depends on prioritizing the collection of high-priority data around the globe, rather than the development of new modeling methods alone.
always_allow_html: true
linkcolor: blue
# header-includes:
#   - \usepackage{draftwatermark}
#   - \SetWatermarkText{DRAFT}
---

@@

<!-- https://www.nature.com/natsustain/about/content -->

<!-- # check in call notes -->

@@

The United Nations Sustainable Development Goal 14 (SDG 14), focusing on "Life under water", calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". Meeting these targets depends in part on our ability to effectively track the status of global marine fish stocks. The Food and Agriculture Organization of the United Nations' (FAO) is the custodian agency of the dedicated SDG 14 Indicator on fisheries sustainability, and the FAO's report on the State of World Fisheries and Aquaculture (SOFIA) report is the most widely used source for tracking the global state of fisheries. As of the most recent report, the FAO estimates that as of 2017 59.6% of marine fish stocks are maximally sustainably fished, 6.2% are underfished, and 34.2% are overfished [@fao2020]. The SOFIA assessment was designed in the 1970s based on the then available data and methods, With the surge in data availability, such as global assessments of management strength, trawl footprints, and fishing effort, and modeling methods,the SOFIA global assessment methods need to be further strengthened to meet the demand for estimation and tracking progress towards the SDG goals.

The FAO's SOFIA index captures 70% of the landings of all fisheries in the world, with statements on on individual stock status made on the basis of formal stock assessments where available, and through a combination of other methods where not [@fao2020]. In this paper we evaluate the ability of alternative data-limited assessment models to improve the methods used by the FAO for these unassessed stocks. While these unassessed stocks are generally individually smaller than the typically larger and more valuable stocks in the assessed category, collectively they are a vital source of food, employment, cultural value, and ecosystem services around the world.

The SOFIA report includes unassessed stocks and bases its estimates for these fisheries on data-limited methods or qualitative expert opinion for each region where these stocks are distributed. While these methods combined with local knowledge can be well informed as to the status of their fish stocks, a more quantitatively vetted process would be desirable in order to increase reproducibility, transparency, and potential reliability. Numerous studies in recent years have put forward versions of "data-limited" models that have attempted to provide estimates for the global status of these unassessed stocks [@costello2012b; @costello2016a; @pauly2007; @rosenberg2018; @thorson2012a]. Due to data limitations, all of these global assessment efforts use forms of "catch-only" stock assessment models (Free et al. 2020 [@free2020] and references therein). These models seek to infer stock status, for example in terms of biomass *B* relative to the biomass at maximum sustainable yield *B~MSY~*, from characteristics of a fishery's catch history, for example the ratio of catch to maximum catch [@martell2013].

@@

Costello et al. 2016 [@costello2016a] finds similar rankings of regions in terms of stock status as RAM, but their estimate of state of fisheries in the Mediterranean/Black Sea regions and Southeast Asia seem to be over-optimistic, and the Northeast Pacific should be better by comparison. The superensemble method [@anderson2017a] used in Rosenberg et al. 2018 [@rosenberg2018] demonstrates the same problem, with stocks in Southeast Asia estimated as doing better than the Northeast Atlantic or Northeast Pacific. The Pauly 2007 [@pauly2007] catch-based approach finds the stocks of Southeast Asia in much better condition than those in the Northeast Pacific or Northeast Atlantic (Table.\@ref(tab:status-tab)). The methods besides RAM in Table.\@ref(tab:status-tab) include both formally assessed and unassessed stocks, and as such we would expect them to differ broadly in their estimates of regional stock status, particularly since we might expect unassessed stocks to be less rigorously managed and by extension have poorer stock status. However, the lack of consistency across heavily assessed regions such as the Northeast Pacific, and the lack of contrast in stock status between heavily and lightly managed regions is concerning.

@@

In this paper we ask, can combining the FAO's catch statistics with other broadly available data improve our understanding of the state of global fisheries? We use a flexible surplus-production based stock assessment software package, [`sraplus`](www.github.com/danovando/sraplus) to demonstrate how different data sources can be used to augment catch-only models at a global scale, and to evaluate how our perception of global stock status would vary depending on which sources of data we include. We show that improving our understanding of the world's unassessed fisheries depends on a redoubled effort at global data collection and synthesis.

@@

| Data Source           |  Short Name | Data Use |  Caveats |
|-----------------------|-------------|------|------|
| Catch data [@fao2020] | catches     | Priors on stock status, scaling of population size, exploitation history    |    Heuristics or regressions used to translate shape of catch history into priors on stock status  |
|    Fisheries Management Index [@melnychuk2017]     | FMI     | Priors on most recent F/F~MSY~ values   |Priors produced by regression trained on data from RAM Legacy Stock Assessment Database|
| Swept Area Ratio [@amoroso2018]      | SAR     | Priors on most recent F/F~MSY~ values |Priors produced by regression trained on data from RAM Legacy Stock Assessment Database|
|  Reconstructed effort data [@rousseau2019b] | effort | Combined with catch data to create an index of abundance| Total reconstructed effort across all sectors. Assumed rate of technology creep reported in individual sections|
Table:(\#tab:data) Data sources included across model fits.

@@

For our case study, we selected `r n_distinct(exs$stockid)` stocks for which we have stock specific FMI and SAR scores. We then paired effort data at the resolution of year, country, and FAO statistical area from Rousseau et al. 2019 [@rousseau2019] to each stock. As a benchmark, we first estimated stock status for these case study fisheries using the CMSY [@froese2017] method, as this has become one of the most widely used catch-only models currently available. We then used stock-specific data on SAR and FMI to generate priors on F/F~MSY~ for each of the stocks, which were then passed to sraplus. Lastly, we used the reconstructed effort data from [@rousseau2019] to create an index of abundance for each stock, and estimated stock status by fitting to this index while using priors on fishing mortality rates informed by each stock's FMI and SAR values. While CMSY systemically overestimated fishing mortality rates and underestimated stock status, use of the SAR, FMI, and effort data produced substantially more accurate results for both B/B~MSY~ and F/F~MSY~ (Fig.\@ref(fig:cs-plot)).

@@

We next assessed the ability of FMI, SAR, and effort data to improve estimates of global stock status. We based this test on `r ram_comp_data$stockid %>% n_distinct()` stocks from RAM, covering `r n_distinct(ram_comp_data$isscaap_group)` broad taxonomic groups, with estimates of B/B~MSY~ and greater than 25 years of continuous catch history. B/B~MSY~ values from RAM are themselves estimates, not data, but they are the best available information on global stock status. We then paired the catch histories for these RAM stocks with regional-level SAR, FMI, and effort data. This process approximates a global-level assessment exercise, where data are available at regional levels, but not for specific fisheries.

@@

Performance limitations then are likely to arise less from model misspecification than from the quality of the data themselves. This becomes clearer once we consider the performance of sraplus models fit to combinations of our broadly available datasets. Many of the datasets used produced similar levels of bias as the RAM data (Table.\@ref(tab:perf-tab)). However, this is somewhat an artifact of the data. The status of most stocks in RAM is also relatively good, with recent B/B~MSY~ values generally near one. This means that a model that more or less reproduces the global average of stock status will be relatively unbiased on average, but imprecise. Focusing on MAPE instead, the error of the models jumps dramatically as soon as data other than RAM are used, to a minimum value of `r percent(perf$mape[2])` and a maximum of `r percent(max(perf$mape))`. The mean accuracy of the sraplus models across all non-RAM data fits was only `r percent(mean(perf$accuracy[!perf$"Data Used" %in% c("ram-data","guess")]))`. Note that there are only three bins in the FAO stock status classifications, and a "model" that randomly assigns a stock to a status category has a mean accuracy of `r percent(perf$accuracy[perf$"Data Used" == "guess"])`.

@@

```{r mpe-map, fig.width=8, fig.height=8, fig.cap="Median percent error in most recent B/B~MSY~ by FAO statistical area from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}
ram_mpe_map_plot
```

```{r mape-map, fig.cap = "Median absolute percent error in most recent B/B~MSY~ by FAO statistical area from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}
ram_mape_map_plot
```

```{r acc-map, fig.cap="Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. RAM Index refers to catch and abundance index drawn from RAM. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for effective a 2.6% technology creep is assumed. RAM U/U~MSY~ assumes all fisheries in the region share a common U/U~MSY~ series with formally assessed fisheries in the region. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assignes a random recent B/B~MSY~ of 0.4,1, or 1.6."}

@@

Global-level assessment are critical for guiding management agendas for the world's oceans, and tracking critical indicators such as the United Nations Sustainable Development Goals. Despite this need, and despite advances in stock assessment methods and available data, we show that our understanding of the world's fisheries remains uncertain in many parts of the world. While in some cases addition of globally available data, such as quality of fisheries management or effort reconstructions, provided value above and beyond catch histories alone (Fig.\@ref(fig:cs-plot)), at the global level models fit using each of the available datasets, besides the RAM-derived indices, produced biased and imprecise estimates of stock status (Table.\@ref(tab:perf-tab)).

@@

We chose to test the performance of methods against estimated values reported in RAM. A reasonable critique of this choice is that unassessed stocks, on which these methods would actually be used, are likely to have vastly different dynamics than the heavily managed stocks in RAM. The clear and systemically poor performance of the methods tested here when applied to RAM stocks would require though that these methods have massively lower bias and higher accuracy for unassessed fisheries than RAM stocks if they are to be expected to provide reasonable picture of global stock status. Free et al. 2020's [@free2020] simulation testing of the types of methods included here suggests that this is unlikely to be true.

@@

Our value-of-information analysis also shows though the high utility of having access to even a recent snapshot of F/F~MSY~ (Fig.\@ref(fig:voi-plot)). Swept area ratios, Fisheries Management Index scores, or other similar metrics can be used to construct priors on fishing mortality rates, though care must be taken in applying them at the appropriate spatial resolution. Another avenue would be to prioritize the development of a global repository for length and age composition data. Given appropriate conditions, these length measurements can be used to estimate local fishing mortality rates [@hordyk2016; @prince2019; @rudd2017]. While length-based assessments come with a host of assumptions and pitfalls, properly implemented in some fisheries with appropriate life histories these methods may provide an overlooked source of information on fisheries at a global scale, at least as an improvement over relying on catch-only or regional proxies alone. Such a database could be used to construct stock or stock complex specific priors on fishing mortality for particular regions around the globe, which could meaningfully improve our understanding of global fisheries, particularly when paired with catch data and where possible indices of abundance [@thorson2015f; @rudd2017].

@@

The core of our model is a Pella-Tomlinson [@pella1969] production model in the manner of [@winker2018]. While models of these kinds abstract away many important details of fish biology and fleet behavior, they are the highest resolution model that the potential data evaluated here will support.
